### 2015-05-14 paper.tex
Typo
more proof progress

@@

Thus, the runtime for the entire algorithm is $O((n^2 + nk)k^{O(\frac{1}{\beta})} + n^3)$.  However, this is only for each time the algorithm is run.  In general, the algorithm must be run once for each possible guess of the expensive clusters, using a brute-force approach.  This requires $n^{O(\frac{1}{\beta e})}$ iterations.  Thus, the overall runtime is $O((n^2 + nk)k^{O(\frac{1}{\beta})}n^{O(\frac{1}{\beta e})})$ which is polynomial.

>>>>

\subsubsection{A given component uniquely contains the inner ring of a given $C^*_i$}

Consider that $T$ contains the inner ring of some $C^*_i$ (which was established above). We show here that all points in $T$ are within $\frac{\beta\text{OPT}}{2|C^*_i|}$ of $c_i^*$, $T \cup B(T)$ are contained in $C_I^*$ and that no other component contains inner ring points from $C^*_i$.

We know all points in $T$ are within $\frac{\beta\text{OPT}}{2|C^*_i|}$ of $c_i^*$ because at least some are in the inner ring of $C^*_i$. Following from \ref{lemma:4.2a} and \ref{emma:4.2b}, it is then impossible for a point to exist that is further than $\frac{\beta\text{OPT}}{2|C^*_i|}$ from $c_i^*$. This immediately implies that $T \subset C_i^*$ because $C_i^*$ is beta distributed. Additionally we have that all points in B(T) are less than $2r$ away from some point in $T$. Because we established $2r = \frac{\beta\text{OPT}}{4s} \leq \frac{\beta\text{OPT}}{2|C_i^*|}$, all points in B(T) then within $ \frac{\beta\text{OPT}}{|C_i^*|}$ of $c_i^*$, and therefor within $C_i^*$.

Because all points in $T$ are sufficiently close to $C_i^*$ there are at most $|C_i^*|$ in $T$, and so $s < 2|C_i^*|$. All inner ring points are at most $\frac{\beta\text{OPT}}{4|C^*_i|} < 2r$ away from any other point, requiring all points not in $T$ be added to $B(T)$. Therefor no other component can contain inner ring points for $C_*^i$.

\subsubsection{Less than $16/(3\beta)$ that do not contain an inner ring point}

Consider a $T$ which does not contain an inner ring point. We will show that all points in $y \in T$ have distance greater than $\frac{3\beta\text{OPT}}{8s}$ to their optimal cluster centers $c_i^*$. Because each $T$ contains at least $s/2$ points, by doing so we show there cannot be more than $16/3\beta$ such $T$ (as their total contribution would then be OPT).

\item Assume $y$ is from an expensive cluster $C^*_i$. Because $Q$ are the set of expensive clusters, we know that for the point to not be thrown out $d(c^*, y) > 2r = \frac{\beta\text{OPT}}{2s} > \frac{3\beta\text{OPT}}{8s}$.

\item $C^*_i$ is a cheaper cluster and $s \geq |C^*|$. Because we established $d(c^*, y) < \frac{\beta \text{OPT}}{2|C^*|}$ or $d(c^*, y) > \frac{3 \beta \text{OPT}}{4|C^*|}$ We know at least one point must meet the larger property. Since the inner ring contains $> |C^*|/2$, but $T$ also contains at least $s/2 = |C^*_i|/2$ points, some point in $T$ must not be in $C^*_i$, and therefor have distance larger than $\frac{3 \beta \text{OPT}}{4|C^*|}$. \ref{lemma:4.2b} then tells us all points must meet the property.

\item $C^*_i$ is a cheaper cluster and $s < |C^*|$. We know that all points are at least $2r$ from the center, as some such component meeting the conditions of the previous section must exist. $d(c^*, y) \geq d(x, y) - d(c^*, x) \geq \frac{\beta\text{OPT}}{2s} - \frac{\beta\text{OPT}}{8|C^*_i|} > \frac{3\beta\text{OPT}}{8s}$
\end{itemize}

@@

Thus, the runtime for the entire algorithm is $O((n^2 + nk)k^{O(\frac{1}{\beta})} + n^3)$.  However, this is only for each time the algorithm is run.  In general, the algorithm must be run once for each possible guess of the expensive clusters, using a brute-force approach.  This requires $n^{O(\frac{1}{\beta e})}$ iterations.  Thus, the overall runtime is $O(((n^2 + nk)k^{O(\frac{1}{\beta})}+n^3)n^{O(\frac{1}{\beta e})}) = O(n^{O(1/\beta\epsilon)}k^{O(1/\beta)}$ .
